Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
New section about algorithmic techniques

>>>>

\medskip
\noindent
\textbf{Algorithmic techniques.} The variant for general $k$ is still unresolved, hence it is vital to summarize algorithmic techniques used in this paper.
A straightforward analysis of the algorithm from Section~\ref{sec:k3} results in the bound $O(\ell^2)$, and the analysis must be improved in two places. One must bound the cost of each of $O(\ell)$ reconfigurations in a phase by a~constant, and show that the optimum offline algorithm must pay for a significant portion of inter-cluster requests.
We bounded the cost of the latter by estimating the capabilities of the optimum offline algorithm to \emph{prepare} for an incoming sequence of requests.
In the analysis of the algorithm from Section~\ref{sec:k2}, we propose a novel charging scheme for intersecting edges.

Furthermore, we state the implications of the tight result for the learning model.
If one hopes to improve the lower bound for the general model, the ground sets must be dynamically added and \emph{removed}: if ground set are only added, the instance is solvable by the algorithm from Section~\ref{sec:ppl} within the cost $O(k\cdot \ell)$.
